### 2021-09-02 input/experiments.tex
first step in styling

\subsection{Confirm the complexity analysis stating that
  communication and time overheads depend on the current partitioning
  of the system.}

\begin{asparadesc}
\item [Description:]

@@

% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
%   system communications.}
\subsection{Confirm that \NAME locks down the traffic of decentralized content
  indexing in the context of dynamic inter-autonomous system
  communications.}

\begin{asparadesc}
\item [Description:]

>>>>

%% \subsection{Confirm the complexity analysis stating that
%%   communication and time overheads depend on the current partitioning
%%   of the system.}

\begin{asparadesc}
\item [Objective:] Confirm the complexity analysis stating that
  communication and time overheads depend on the current partitioning
  of the system.

\item [Description:]

@@

%% \subsection{Confirm that \NAME locks down the traffic of decentralized content
%%   indexing in the context of dynamic inter-autonomous system
%%   communications.}

\begin{asparadesc}

\item [Objective:] Confirm that \NAME locks down the traffic of decentralized content
  indexing in the context of dynamic inter-autonomous system
  communications.

\item [Description:]
